\subsection{Definition of Done}\label{sec:dod}
The team established the following criteria on \textbf{10 June 2026}. A Phase~1 checkpoint or
deliverable is considered \emph{done} when all applicable items below are satisfied.

\subsubsection{Documentation Criteria}
\begin{itemize}
  \item Content reflects decisions made in team discussion (see \texttt{discussions/} in the repository).
  \item Technical writing is merged into \texttt{docs/module/} (modular \texttt{.tex} files) and compiles without errors.
  \item Section owners verify accuracy before the item is marked complete in the checkpoint list.
\end{itemize}

\subsubsection{Collaboration Criteria}
\begin{itemize}
  \item Work is committed on a feature branch and merged via pull request---not pushed directly to \texttt{main}.
  \item Discussion notes and LaTeX documentation may land on separate branches and are integrated independently.
  \item At least one teammate reviews the pull request before merge.
\end{itemize}

\subsubsection{Checkpoint Exit Criteria}
\begin{itemize}
  \item \textbf{Task Breakdown} --- All four epics documented with task IDs (Section~\ref{sec:tasks}).
  \item \textbf{Database Modeling} --- ERD, data dictionary, and integrity rules agreed upon (Section~\ref{sec:database}).
  \item \textbf{API Contract} --- Every endpoint from the task breakdown has request/response bodies and HTTP status codes (Section~\ref{sec:api}).
  \item \textbf{Task Backlog} --- Remaining Phase~1 items tracked in GitHub Issues or Projects (Section~\ref{sec:task-backlog}).
\end{itemize}

\subsubsection{Phase 1 Completion}
As of 11 June 2026, all Phase~1 checkpoints are complete. The team may proceed to Phase~2 once all
members have reviewed Sections~\ref{sec:tasks}--\ref{sec:api}.

\subsubsection{Phase 2 Progress}
Phase~2 completed 12 June 2026. All deliverables meet the documentation and collaboration criteria
and are recorded in the task backlog.
\begin{itemize}
  \item \textbf{UI Wireframing} --- Complete: Login, Register, Dashboard, and navigation flow (Section~\ref{sec:wireframes}).
  \item \textbf{Component Design} --- Complete: routes, component tree, and service layer agreed (Section~\ref{sec:task-backlog}).
  \item \textbf{LaTeX refactor} --- Complete: modular \texttt{docs/module/} layout, section introductions, expanded sequence diagrams.
  \item \textbf{System Architecture} --- Complete: data-flow documentation merged.
  \item \textbf{Security Planning} --- Complete: JJWT and auth-interceptor design agreed.
\end{itemize}

\subsubsection{Phase 3 Completion}
Phase~3 (Backend Development) completed 22 June 2026. All checkpoints satisfied:
\begin{itemize}
  \item \textbf{Project Scaffolding} --- Spring Boot 4.1.0, Gradle Kotlin DSL, SQLite configured.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/46}{\#46},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/45}{\#45},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/44}{\#44}
  \item \textbf{Data Layer} --- JPA entities (User, Task, Subtask), repositories with UUID keys.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/49}{PR~\#49}
  \item \textbf{Security Implementation} --- JWT via JJWT 0.13.0, HandlerInterceptor, PasswordValidator.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/51}{\#51},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/40}{PR~\#40}
  \item \textbf{Business Logic} --- Registration, login, task CRUD, subtask CRUD with ownership enforcement.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/11}{\#11},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/50}{\#50},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/55}{PR~\#55},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/56}{PR~\#56}
  \item \textbf{Design Validation} --- All 11 endpoints verified via cURL (45 test cases, all passing).
\end{itemize}

\subsubsection{Phase 4 Completion}
Phase~4 (Frontend Development) completed 25 June 2026. All checkpoints satisfied:
\begin{itemize}
  \item \textbf{Project Scaffolding} --- Angular 22 standalone components, Vitest, proxy config.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/54}{\#54}
  \item \textbf{Service Layer} --- TaskService, SubtaskService, AuthService with signal-based state.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/62}{PR~\#62},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/63}{PR~\#63}
  \item \textbf{Auth Integration} --- Functional interceptor, route guard, login/register components.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/59}{PR~\#59},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/60}{PR~\#60},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/58}{PR~\#58}
  \item \textbf{Task Management UI} --- Dashboard with inline edit, expand/collapse subtasks, CRUD.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/64}{PR~\#64}
  \item \textbf{Design Validation} --- UI matches wireframes; end-to-end workflow verified.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/67}{PR~\#67}
\end{itemize}

\subsubsection{Phase 5 Status}
Phase~5 (Presentation) is \emph{ready} as of 26 June 2026.
\begin{itemize}
  \item \textbf{Functional Demo} --- All user stories operational; happy-path scenarios verified.
  \item \textbf{Technical Review} --- Data flow, schema design, and architecture documented.
  \item \textbf{Build Verification} --- Clean build confirmed (\texttt{gradlew build}, \texttt{ng build}).
  \item \textbf{Post-Mortem} --- Agile process, Git workflow, and blockers documented in project records.
\end{itemize}

\newpage
