\subsection{Task Backlog}\label{sec:task-backlog}
Use GitHub Issues and Github Project to track actionable items. Phase~1 completed \textbf{11 June 2026};
Phase~2 completed \textbf{12 June 2026}; Phase~3 completed \textbf{22 June 2026};
Phase~4 completed \textbf{25 June 2026}; Phase~5 ready \textbf{26 June 2026}.
Session summaries below record how each phase was closed out.

\subsubsection{Session Summary --- 10 June 2026}
\begin{tabularx}{\textwidth}{@{} l X @{}}
  \toprule
  \textbf{Activity} & \textbf{Outcome} \\
  \midrule
  LaTeX documentation initiated & Jaehoon Song set up the \texttt{docs/} structure and \texttt{main.tex} driver. \\
  Team meeting --- task breakdown & All members decomposed user stories into epics and task IDs; documented in Section~\ref{sec:tasks}. \\
  Initial ERD & Jaehoon Song drafted the Crow's Foot ERD and SQLite data dictionary (Section~\ref{sec:database}). \\
  Repository integration & Each member used feature branches to merge discussion notes and LaTeX updates separately into \texttt{main}. \\
  Definition of Done & Team agreed on completion criteria (Section~\ref{sec:dod}). \\
  Task Backlog & Initial Phase~1 progress and GitHub workflow recorded (Section~\ref{sec:task-backlog}). \\
  \bottomrule
\end{tabularx}

\subsubsection{Session Summary --- 11 June 2026}
\begin{tabularx}{\textwidth}{@{} l X @{}}
  \toprule
  \textbf{Activity} & \textbf{Outcome} \\
  \midrule
  API Contract & Daniel Patience and Jacqueline Lainhart drafted payloads and status codes; documented in Section~\ref{sec:api}. \\
  HTTP request/response documentation & Jaehoon Song formatted API exchanges as HTTP traces (\texttt{httpexchange} layout); Section~\ref{sec:api}. \\
  Phase 1 completion & All Phase~1 checkpoints satisfied; team cleared to begin Phase~2 (Section~\ref{sec:dod}). \\
  \bottomrule
\end{tabularx}

\subsubsection{Session Summary --- 12 June 2026}
\begin{tabularx}{\textwidth}{@{} l X @{}}
  \toprule
  \textbf{Activity} & \textbf{Outcome} \\
  \midrule
  LaTeX documentation refactor & Jaehoon Song reorganized content into \texttt{docs/module/}, added section introductions in \texttt{main.tex}, and expanded Epic~3/4 sequence diagrams (Section~\ref{sec:seq-diagrams}). \\
  UI Wireframing & Login, Register, Dashboard, and screen-navigation wireframes added to \texttt{docs/Wireframes/} and documented in Section~\ref{sec:wireframes}. \\
  Component Design & Team agreed Angular routes (\texttt{/}, \texttt{/register}, \texttt{/dashboard}), component hierarchy (\texttt{AppComponent}, auth views, \texttt{TodoItemComponent} with nested subtasks), and services (\texttt{AuthService}, \texttt{TodoService}, \texttt{SubtaskService}, \texttt{AuthInterceptor}, \texttt{AuthGuard}). \\
  Phase 2 completion & All Phase~2 checkpoints and deliverables satisfied; team cleared to begin Phase~3 (Section~\ref{sec:dod}). \\
  \bottomrule
\end{tabularx}

\subsubsection{GitHub Workflow}
\begin{enumerate}
  \item Create a branch from \texttt{main} for the work item (discussion notes or documentation).
  \item Commit changes locally; open a pull request when ready for review.
  \item A teammate reviews and approves; merge into \texttt{main}.
  \item Open or update a GitHub Issue for any remaining task IDs; link the issue to the pull request where applicable.
\end{enumerate}

\subsubsection{Backlog Status --- Phase 1 (complete 11 June 2026)}
\begin{tabularx}{\textwidth}{@{} l l X @{}}
  \toprule
  \textbf{Item} & \textbf{Status} & \textbf{Notes} \\
  \midrule
  Task Breakdown (Section~\ref{sec:tasks})       & Complete & Documented from team meeting discussion; 10 June 2026. \\
  Database Modeling (Section~\ref{sec:database}) & Complete & Initial ERD and data dictionary; 10 June 2026. \\
  API Contract (Section~\ref{sec:api})          & Complete & Payloads by Daniel Patience and Jacqueline Lainhart; HTTP req/res traces by Jaehoon Song; 11 June 2026. \\
  Definition of Done (Section~\ref{sec:dod})     & Complete & Criteria established; 10 June 2026. \\
  GitHub Issues / Project board                  & Complete & Workflow recorded; issues to be opened as Phase~3 work is assigned. \\
  \bottomrule
\end{tabularx}

\subsubsection{Backlog Status --- Phase 2 (complete 12 June 2026)}
\begin{tabularx}{\textwidth}{@{} l l X @{}}
  \toprule
  \textbf{Item} & \textbf{Status} & \textbf{Notes} \\
  \midrule
  System Architecture (Appendix~A) & Complete & Data flow documented in \texttt{discussions/phase-2-deliverables.md}; 12 June 2026. \\
  Security Planning (Appendix~A) & Complete & JJWT and auth approach agreed; 12 June 2026. \\
  UI Wireframing (Section~\ref{sec:wireframes})   & Complete & Four wireframes under \texttt{docs/Wireframes/}; 12 June 2026. \\
  Component Design (Appendix~A) & Complete & Routes, component tree, and services agreed; 12 June 2026. \\
  LaTeX documentation refactor                   & Complete & Modular \texttt{docs/module/} structure and section intros; 12 June 2026. \\
  API Specification (Section~\ref{sec:api})       & Complete & Finalized for implementation; 12 June 2026. \\
  Database Schema (Section~\ref{sec:database})   & Complete & ERD and data dictionary signed off; 12 June 2026. \\
  \bottomrule
\end{tabularx}

\subsubsection{Session Summary --- 16 June 2026}
\begin{tabularx}{\textwidth}{@{} l X @{}}
  \toprule
  \textbf{Activity} & \textbf{Outcome} \\
  \midrule
  Spring Boot scaffolding & Kiro-assisted project initialization with Gradle Kotlin DSL, SQLite, JPA.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/46}{\#46} \\
  Ignore rules and steerings & Configured \texttt{.gitignore} and Kiro steering files for team workflow.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/45}{\#45},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/44}{\#44} \\
  Password requirements & Daniel Patience documented password validation rules.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/40}{PR~\#40} \\
  \bottomrule
\end{tabularx}

\subsubsection{Session Summary --- 19 June 2026}
\begin{tabularx}{\textwidth}{@{} l X @{}}
  \toprule
  \textbf{Activity} & \textbf{Outcome} \\
  \midrule
  JPA entities and repositories & Jacqueline Lainhart ran Kiro Phase~3 tasks for entity setup.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/49}{PR~\#49} \\
  Feature issues created & Opened spec-driven issues for registration, auth, and task CRUD.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/50}{\#50},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/51}{\#51},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/52}{\#52} \\
  \bottomrule
\end{tabularx}

\subsubsection{Session Summary --- 22 June 2026}
\begin{tabularx}{\textwidth}{@{} l X @{}}
  \toprule
  \textbf{Activity} & \textbf{Outcome} \\
  \midrule
  Registration spec and implementation & Jacqueline Lainhart delivered registration spec and ran tasks.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/55}{PR~\#55},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/11}{\#11 closed} \\
  Task/Subtask CRUD & Daniel Patience implemented TaskService, SubtaskService, controllers.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/53}{PR~\#53},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/56}{PR~\#56} \\
  Frontend issue opened & Angular frontend work tracked under single issue.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/54}{\#54} \\
  \bottomrule
\end{tabularx}

\subsubsection{Session Summary --- 23 June 2026}
\begin{tabularx}{\textwidth}{@{} l X @{}}
  \toprule
  \textbf{Activity} & \textbf{Outcome} \\
  \midrule
  Registration tasks completed & Jacqueline Lainhart fixed DTO/bcrypt issues and ran registration tasks.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/57}{PR~\#57},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/58}{PR~\#58} \\
  Authentication spec and draft & Jaehoon Song created Kiro spec for US02, drafted auth feature.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/59}{PR~\#59},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/60}{PR~\#60} \\
  Entity alignment & Daniel Patience renamed userId fields, aligned folder structure.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/61}{PR~\#61} \\
  Frontend specs & Jaehoon Song added client01 auth-integration spec; Daniel added dashboard specs.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/62}{PR~\#62},
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/63}{PR~\#63} \\
  \bottomrule
\end{tabularx}

\subsubsection{Session Summary --- 24--25 June 2026}
\begin{tabularx}{\textwidth}{@{} l X @{}}
  \toprule
  \textbf{Activity} & \textbf{Outcome} \\
  \midrule
  Full frontend implementation & Jacqueline Lainhart delivered Angular app: auth, dashboard, services.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/64}{PR~\#64} \\
  Build fixes & Jaehoon Song fixed ignore rules to exclude DB binaries.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/66}{PR~\#66} \\
  UI/UX polish & Jacqueline Lainhart finalized styling and responsiveness.
    \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/67}{PR~\#67} \\
  Phase 4 complete & End-to-end workflow verified; all user stories functional. \\
  \bottomrule
\end{tabularx}

\subsubsection{Backlog Status --- Phase 3 (complete 22 June 2026)}
\begin{tabularx}{\textwidth}{@{} l l X @{}}
  \toprule
  \textbf{Item} & \textbf{Status} & \textbf{Notes} \\
  \midrule
  Project Scaffolding & Complete & Spring Boot 4.1.0, Gradle, SQLite; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/46}{\#46} \\
  Data Layer          & Complete & User, Task, Subtask JPA entities; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/49}{PR~\#49} \\
  Security            & Complete & JWT + HandlerInterceptor; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/60}{PR~\#60} \\
  Business Logic      & Complete & All CRUD services; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/56}{PR~\#56} \\
  Design Validation   & Complete & 45 curl tests passing; API contract synced 26 June 2026 \\
  \bottomrule
\end{tabularx}

\subsubsection{Backlog Status --- Phase 4 (complete 25 June 2026)}
\begin{tabularx}{\textwidth}{@{} l l X @{}}
  \toprule
  \textbf{Item} & \textbf{Status} & \textbf{Notes} \\
  \midrule
  Angular Scaffolding & Complete & Angular 22, standalone components; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/issues/54}{\#54} \\
  Service Layer       & Complete & TaskService, SubtaskService; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/63}{PR~\#63} \\
  Auth Integration    & Complete & AuthService, interceptor, guard; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/62}{PR~\#62} \\
  Task Management UI  & Complete & Dashboard with inline edit, subtask expand; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/64}{PR~\#64} \\
  Design Validation   & Complete & Matches wireframes; \href{https://github.com/JaehoonSong12/PEP-Team02-TheDJs/pull/67}{PR~\#67} \\
  \bottomrule
\end{tabularx}

\subsubsection{Backlog Status --- Phase 5 (ready 26 June 2026)}
\begin{tabularx}{\textwidth}{@{} l l X @{}}
  \toprule
  \textbf{Item} & \textbf{Status} & \textbf{Notes} \\
  \midrule
  Functional Demo     & Ready & All user stories operational \\
  Technical Review    & Ready & Data flow, schema, architecture documented \\
  Build Verification  & Ready & \texttt{gradlew build} and \texttt{ng build} confirmed \\
  Post-Mortem         & Ready & Agile process and blockers recorded in session summaries above \\
  \bottomrule
\end{tabularx}

\newpage
