% Project-wide context — included once before phase modules.

\section{Project Overview}\label{sec:overview}
\SetDocHeader{Project Overview}

\subsection{Objective}
Build a full-stack, secure Todo Management application as part of the Revature full-stack
SDLC training program. The team moves from initial requirement analysis to a functional
product demonstration, simulating a real-world Software Development Lifecycle (SDLC).

\subsection{Technology Stack}
\begin{tabularx}{\textwidth}{@{} l X @{}}
\toprule
\textbf{Layer} & \textbf{Technology} \\
\midrule
Frontend       & Angular \\
Backend        & Java (Spring Boot, Web, Data JPA) \\
Database       & SQLite \\
Build / Tools  & Gradle, Git, GitHub \\
\bottomrule
\end{tabularx}

\subsection{User Stories (Scope)}
The following stories define \emph{what} the system must deliver. Each phase builds on
the prior phase toward a complete implementation.

\begin{enumerate}
  \item \textbf{Registration:} As a new user, I can register an account.
  \item \textbf{Authentication:} As a user, I can log in and log out securely.
  \item \textbf{Task Management:} As a user, I can create, read, update, and delete primary Todo items.
  \item \textbf{Organization:} As a user, I can create, read, update, and delete nested subtasks.
\end{enumerate}

\subsection{Project Roadmap}
\begin{tabularx}{\textwidth}{@{} c l X @{}}
\toprule
\textbf{Phase} & \textbf{Name} & \textbf{Goal} \\
\midrule
1 & Requirements Analysis & Deconstruct user stories; define schema and API contracts. \\
2 & Design                & Plan architecture, wireframes, and security flows. \\
3 & Backend Development   & Build REST API, security layer, and persistence. \\
4 & Frontend Development  & Build Angular UI and integrate with the API. \\
5 & Presentation          & Demonstrate working software and architecture. \\
\bottomrule
\end{tabularx}

\newpage
