% Phase 2: Design

\PhaseTitlePage{2}{Design}{TMA-DES-P2}{Design Document}

\section{Phase 2: Design}\label{sec:phase2}
\SetDocHeader{Phase 2: Design}

\subsection{Objective}
The goal of this phase is architectural and interface planning. The team must define the data flow,
security protocols, and user interface layouts. Successful completion of this phase ensures that
the Backend and Frontend teams can work in parallel without integration conflicts.

\subsubsection{Checkpoints}
\begin{itemize}
  \item[$\square$] \textbf{System Architecture:} Document the data flow (Angular $\rightarrow$ Spring Boot $\rightarrow$ SQLite).
  \item[$\square$] \textbf{Security Planning:} Familiarize yourself with JJWT.
  \item[$\square$] \textbf{UI Wireframing:} Map out the interface for authentication and task management.
  \item[$\square$] \textbf{Component Design:} Loosely define the Angular component hierarchy and service structure.
\end{itemize}

\subsection{Technical Reference: Design Standards}

\subsubsection{API Design Principles}
All endpoints must follow RESTful conventions. Use the following templates for your design documentation:

\subsubsection{Resource Creation Flow (Template)}
Use this logic to design your \texttt{POST} endpoints to ensure consistent error handling
(e.g., handling duplicate entries).
\begin{enumerate}[label=\arabic*., nosep, leftmargin=*]
  \item Client/Requester sends a Create Request to the API/Interface Layer.
  \item API forwards the request to the Business Logic Layer for processing.
  \item[\textbf{A.}] Resource is unique: Logic checks existence via Data Access $\rightarrow$ Storage (not found); persists the new resource; returns a 2xx Success Response to the client.
  \item[\textbf{B.}] Conflict / already exists: Logic checks existence (found); signals conflict to API; returns a 4xx Error Response to the client.
\end{enumerate}

\subsubsection{Login/Auth Flow (Template)}
Use this logic to design your \texttt{/auth} endpoints to ensure secure credential validation.
\begin{enumerate}[label=\arabic*., nosep, leftmargin=*]
  \item Client/Requester sends a Login Request to the API/Interface Layer.
  \item API forwards the request to the Business Logic Layer.
  \item[\textbf{A.}] Success: Logic fetches user data via Data Access $\rightarrow$ Storage; Utility validates credentials and generates a token; API returns a 2xx Success Response with token.
  \item[\textbf{B.}] Invalid credentials: Logic fetches user data (null/empty); API returns a 4xx Error Response to the client.
\end{enumerate}

\subsubsection{Deliverables for Phase 2}
By the end of this phase, your team should have:
\begin{enumerate}
  \item \textbf{API Specification:} A completed document defining all endpoints, request bodies, and response codes.
  \item \textbf{Wireframes:} Visual mockups of the Login, Register, and Dashboard screens.
  \item \textbf{Database Schema:} A final relational model (ERD) ready for implementation.
\end{enumerate}

\subsubsection{Moving to Phase 3}
Once the API contracts and UI wireframes are finalized and agreed upon by all team members,
proceed to \textbf{Phase 3: Backend Development}.

\newpage
