% Phase 1: Requirements Analysis — Todo Management Application
% Compile: pdflatex main.tex (run twice for TOC/refs)

\documentclass{article}
\hbadness=10000
\vbadness=10000

% -------------------------------------------------------------------
% PACKAGES
% -------------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[english]{babel}

\usepackage[margin=1in]{geometry}
\usepackage{parskip}

\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,fit,backgrounds,shadows,arrows.meta,calc,babel}

\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{enumitem}
\usepackage{amssymb}
\usepackage{listings}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Phase 1 Requirements Analysis \textbar\ Todo Management Application}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  urlcolor=blue,
  pdftitle={Todo Management Application — Phase 1},
  pdfauthor={Jaehoon Song, Daniel Patience, Jacqueline Lainhart}
}

\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  columns=fullflexible,
  showstringspaces=false
}

% -------------------------------------------------------------------
\begin{document}
% -------------------------------------------------------------------

\begin{titlepage}
  \thispagestyle{empty}
  \centering
  \vspace*{2.5cm}
  {\LARGE\bfseries Phase 1: Requirements Analysis\par}
  \vspace{1.2cm}
  {\Large Todo Management Application\par}
  \vspace{0.6cm}
  {\large Full-Stack SDLC Project Document\par}
  \vspace{2.5cm}
  {\large
    Jaehoon Song \\
    Daniel Patience \\
    Jacqueline Lainhart
  \par}
  \vspace{2cm}
  \begin{tabular}{@{}r@{\hspace{1.5em}}l@{}}
    \textbf{Document version:} & 0.1 (Draft) \\
    \textbf{Status:}           & In Progress \\
    \textbf{Phase:}            & 1 of 5 \\
    \textbf{Date:}             & \today \\
  \end{tabular}
  \vfill
  {\small Angular \textbullet\ Spring Boot \textbullet\ SQLite \textbullet\ Gradle\par}
\end{titlepage}

\tableofcontents




\newpage
% -------------------------------------------------------------------
\section{Project Overview}\label{sec:overview}
% -------------------------------------------------------------------

\subsection{Objective}
Build a full-stack, secure Todo Management application using Agile methodologies.
The team moves from initial requirement analysis to a functional product demonstration,
simulating a real-world Software Development Lifecycle (SDLC).

\subsection{Technology Stack}
\begin{tabularx}{\textwidth}{@{} l X @{}}
\toprule
\textbf{Layer} & \textbf{Technology} \\
\midrule
Frontend       & Angular \\
Backend        & Java (Spring Boot, Web, Data JPA) \\
Database       & SQLite \\
Build / Tools  & Gradle, Git, GitHub \\
\bottomrule
\end{tabularx}

\subsection{User Stories (Scope)}
The following stories define \emph{what} the system must deliver. Phase~1 decomposes
each story into technical tasks, data structures, and API contracts.

\begin{enumerate}
  \item \textbf{Registration:} As a new user, I can register an account.
  \item \textbf{Authentication:} As a user, I can log in and log out securely.
  \item \textbf{Task Management:} As a user, I can create, read, update, and delete primary Todo items.
  \item \textbf{Organization:} As a user, I can create, read, update, and delete nested subtasks.
\end{enumerate}

\subsection{Project Roadmap}
\begin{tabularx}{\textwidth}{@{} c l X @{}}
\toprule
\textbf{Phase} & \textbf{Name} & \textbf{Goal} \\
\midrule
1 & Requirements Analysis & Deconstruct user stories; define schema and API contracts. \\
2 & Design                & Plan architecture, wireframes, and security flows. \\
3 & Backend Development   & Build REST API, security layer, and persistence. \\
4 & Frontend Development  & Build Angular UI and integrate with the API. \\
5 & Presentation          & Demonstrate working software and architecture. \\
\bottomrule
\end{tabularx}

\newpage
% -------------------------------------------------------------------
\section{Phase 1 Objectives and Checkpoints}\label{sec:phase1}
% -------------------------------------------------------------------

\subsection{Objective}
Decompose user stories into granular technical work \emph{before} any implementation begins.
The team must agree on data structures, API communication standards, and completion criteria.

\subsection{Phase 1 Checkpoints}
Use this checklist to track phase completion. Mark each item when the deliverable is reviewed
and accepted by the team.

\begin{itemize}
  \item[$\square$] \textbf{Task Breakdown} — User stories decomposed into assignable technical tasks.
  \item[$\square$] \textbf{Database Modeling} — Relational schema for User, Todo, and Subtask entities.
  \item[$\square$] \textbf{API Contract} — RESTful endpoints with JSON request/response bodies.
  \item[$\square$] \textbf{Definition of Done} — Team-specific criteria for completed work.
\end{itemize}

\subsection{Phase 1 Deliverables}
\begin{enumerate}
  \item \textbf{Entity Relationship Diagram (ERD)} — Visual or text-based SQLite schema.
  \item \textbf{API Specification} — Endpoint list with payloads and status codes.
  \item \textbf{Task Backlog} — Actionable items tracked in GitHub Issues and Projects.
\end{enumerate}

\subsection{Exit Criteria (Moving to Phase 2)}
Proceed to Phase~2 when:
\begin{itemize}
  \item All checkpoints above are complete.
  \item The team has reviewed and signed off on the ERD and API contract.
  \item Backlog items are created in GitHub and assigned or ready for assignment.
\end{itemize}




\end{document}
