% Phase 1 instructions (appendix).
\section{Phase 1: Requirements Analysis}\label{sec:phase1}
\SetDocHeader{Phase 1: Requirements Analysis}

\subsection{Objective}
The goal of this phase is the technical decomposition of user stories. Before any code is written,
the team must define the data structures, the API communication standards, and the criteria for
successful completion.

\subsection{Checkpoints}
\begin{itemize}
  \item[$\checkmark$] \textbf{Task Breakdown:} Deconstruct user stories into granular technical tasks.
  \item[$\checkmark$] \textbf{Database Modeling:} Design the relational schema (User, Todo, and Subtask entities).
  \item[$\checkmark$] \textbf{API Contract:} Define RESTful endpoints and expected JSON request/response bodies.
  \item[$\checkmark$] \textbf{Definition of Done (DoD):} Establish team-specific criteria for completed work.
\end{itemize}

\subsection{Technical Reference: User Stories}
Use these stories as the foundation for your task breakdown and API design:
\begin{enumerate}
  \item \textbf{Account Creation:} As a new user, I can register an account to start tracking my todo tasks.
  \item \textbf{Authentication:} As a new user, I can log in and out to securely access my todo items.
  \item \textbf{Task Management:} As a user, I can create, edit, and delete todo items to keep track of my work.
  \item \textbf{Subtask Organization:} As a user, I can create, edit, and delete subtask items to better organize my primary tasks.
\end{enumerate}

\subsection{Deliverables for Phase 1}
By the end of this phase, your team should have a shared document or repository folder containing:
\begin{enumerate}
  \item \textbf{Entity Relationship Diagram (ERD):} Visual or text-based representation of your SQLite schema.
  \item \textbf{API Specification:} A list of endpoints (e.g., \texttt{POST /api/auth/register}, \texttt{GET /api/todos}) including expected payloads.
  \item \textbf{Task Backlog:} A list of specific, actionable items ready to be assigned to team-members.
  \begin{itemize}
    \item Use GitHub Issues and Github Project to facilitate this.
  \end{itemize}
\end{enumerate}

\subsection{Moving to Phase 2}
Once all Phase~1 checkboxes are marked as complete and the team agrees on the API contracts,
proceed to \textbf{Phase 2: Design}.
