\newpage
% Phase 3 instructions (appendix).
\section{Phase 3: Backend Development}\label{sec:phase3}
\SetDocHeader{Phase 3: Backend Development}

\subsection{Objective}
The goal of this phase is to build a robust, secure REST API. This phase focuses on the
``engine'' of the application: data persistence, business logic, and security. The backend
must be fully functional and testable via tools like Postman or cURL before the frontend development begins.

\subsection{Checkpoints}
\begin{itemize}
  \item[$\square$] \textbf{Project Scaffolding:} Initialize Gradle, Spring Boot, and SQLite configuration.
  \item[$\square$] \textbf{Data Layer:} Implement Spring Data JPA repositories and entity mappings.
  \item[$\square$] \textbf{Security Implementation:} Build the authentication and authorization logic.
  \item[$\square$] \textbf{Business Logic:} Develop required CRUD services for all entities.
  \item[$\square$] \textbf{Design Validation:} Confirm all implemented endpoints and data models match Phase~1/2 specifications.
\end{itemize}

\subsection{Technical Requirements}

\subsubsection{API Compliance}
All developed endpoints \textbf{must} match the API Contract defined in Phase~1/2. Any deviation from
the agreed-upon JSON structure or endpoint path must be approved by the team before implementation.

\subsubsection{Security Standards}
\begin{itemize}
  \item \textbf{Authentication:} Ensure all protected routes (Todo/Subtask management) require a valid user session or token.
  \item \textbf{Authorization:} Ensure users can only access, edit, or delete data that belongs to their own account.
\end{itemize}

\subsubsection{Error Handling}
The API must return meaningful HTTP status codes:
\begin{itemize}
  \item \texttt{200 OK} / \texttt{201 Created}: Successful operations.
  \item \texttt{400 Bad Request}: Validation errors (e.g., missing required fields).
  \item \texttt{401 Unauthorized}: Missing or invalid authentication.
  \item \texttt{403 Forbidden}: Authenticated user attempting to access unauthorized data.
  \item \texttt{404 Not Found}: Resource does not exist.
\end{itemize}

\subsection{Deliverables for Phase 3}
By the end of this phase, your team should have:
\begin{enumerate}
  \item \textbf{Functional REST API:} A running Spring Boot application.
  \item \textbf{Verified Endpoints:} A collection of successful tests (via Postman, cURL, or similar) demonstrating all CRUD operations.
  \item \textbf{Persisted Data:} Evidence that data persists in the SQLite database after application restarts.
\end{enumerate}

\subsection{Moving to Phase 4}
Once the backend is stable and the API endpoints are verified,
proceed to \textbf{Phase 4: Frontend Development}.


\medskip
\noindent\rule{\linewidth}{0.4pt}
\medskip


\subsection{Project Scaffolding}\label{sec:be-scaffolding}
Initialize Gradle, Spring Boot, and SQLite configuration.
See deliverable checklist in Section~\ref{sec:phase3}.

\subsection{Data Layer}\label{sec:data-layer}
Implement Spring Data JPA repositories and entity mappings.
See deliverable checklist in Section~\ref{sec:phase3}.

\subsection{Security Implementation}\label{sec:security-impl}
Build the authentication and authorization logic.
See deliverable checklist in Section~\ref{sec:phase3}.

\subsection{Business Logic}\label{sec:business-logic}
Develop required CRUD services for all entities.
See deliverable checklist in Section~\ref{sec:phase3}.

\subsection{Design Validation}\label{sec:be-design-validation}
Confirm all implemented endpoints and data models match Phase~1/2 specifications.
See deliverable checklist in Section~\ref{sec:phase3}.

\subsection{Functional REST API}\label{sec:functional-api}
Document the running Spring Boot application.
See deliverable checklist in Section~\ref{sec:phase3}.

\subsection{Verified Endpoints}\label{sec:verified-endpoints}
Record successful tests (via Postman, cURL, or similar) demonstrating all CRUD operations.
See deliverable checklist in Section~\ref{sec:phase3}.

\subsection{Persisted Data}\label{sec:persisted-data}
Provide evidence that data persists in the SQLite database after application restarts.
See deliverable checklist in Section~\ref{sec:phase3}.
